### 2022-05-15 manuscript/manuscript.Rmd
AmStat round 2 revisions

```{r load_packages}
library(papaja) # for article template
library(knitr) # for literate programming
library(tidyverse) # for data munging
library(janitor) # for data munging
#library(tidylog) # inline code feedback
library(here) # for finding files
library(assertr) # for testing
library(scales) # to colour palette
library(patchwork) # for multipanel figures
library(kableExtra) # for latex tables
```

@@

```{r set_defaults}
# define a custom colour palette that links specific colours to specific scientific disciplines across graphs
scale_fill_domains <- function(...){
    ggplot2:::manual_scale(
        'fill', 
        values = setNames(c(hue_pal()(22),'#000000'), c(levels(factor(sum_tab_topics$esi_abbr[! sum_tab_topics$esi_abbr == 'OVERALL'])), 'OVERALL')), 
        ...
    )
}
```

@@

It is unclear whether journal-based statistical guidance, advocacy, or regulation is helpful or detrimental, especially in the context of controversial statistical topics (Mayo, 2021). There continues to be heated debate among statisticians and methodologists about fundamental statistical issues, as exemplified by the diverse commentaries in a 2019 special issue of The American Statistician (Wasserstein et al., 2019). P-values continue to be vigorously attacked (Wagenmakers, 2007) and staunchly defended (Mayo, 2018), and recent years have seen competing calls to either abandon (McShane et al., 2019), redefine (Benjamin et al., 2018), or justify (Lakens et al., 2018) statistical significance. Others have advocated for a so-called “New Statistics” centered on effect size estimation and confidence intervals (Cumming, 2014) or promoted wider adoption of Bayesian statistics (Goodman, 1999; Kruschke & Liddell, 2018).

In some cases, these debates have influenced journal policy and drastic changes in policy have sometimes backfired. For example, in 2005, in an attempt to avoid the “pitfalls of traditional statistical inference”, the journal Psychological Science endorsed a novel statistic prep (Killeen, 2005) which was subsequently adopted by the majority of publishing authors, and then abandoned under heavy criticism a few years later (Iverson et al., 2009). In 2015, the journal Basic and Applied Social Psychology introduced an outright ban on p-values and confidence intervals “because the state of the art remains uncertain” (Trafimow & Marks, 2015). An assessment of articles published in the first year after the ban argued that the absence of statistical safeguards led many authors to overstate their findings (Fricker et al., 2019). 
Although particularly controversial journal policies easily catch our attention, they may not be representative. Currently there is limited empirical data documenting the prevalence and content of statistical guidance for authors issued by scientific journals. Such data may help to inform debates about the appropriate role of journal policy in addressing statistical issues (Mayo, 2021) as well as identify gaps in journal-based statistical guidance within and across scientific disciplines. Some previous research has addressed this topic and suggested that there is probably large room for improvement. For example, Schriger et al. (2006) reported that 39% of 166 leading medical journals provided statistical guidance to authors. Topics addressed included p-values (20%), confidence intervals (14%), statistical power (10%), multiple testing (5%), modeling (4%), sensitivity analysis (4%), and Bayesian methods (1%). Recently, Malicki et al. (2019) used a text-mining approach to search for a limited set of terms related to Bayes factors, confidence intervals, effect sizes, and sample size calculations in instructions to authors provided by 835 journals across a range of scientific disciplines. The prevalence of any statistical guidance, defined by these terms, was 6% across all journals. Another empirical evaluation (Malicki et al., 2020) found that none of 57 preprint servers provided any statistical advice. These three studies provide some insight into the prevalence and content of statistical guidance offered to authors; however, Schriger et al. (2006) was limited to medical journals, Malicki et al. (2020) was limited to preprint servers, and Malicki et al. (2019) focused on only a few statistical topics.

@@

Across all 22 scientific fields (n = 330 journals), the median 2017 Journal Impact Factor was `r allFieldChar %>% pull(Median_jif)` (IQR = `r allFieldChar %>% pull(IQR_jif)`; range `r allFieldChar %>% pull(Min_jif)` - `r allFieldChar %>% pull(Max_jif)`). Journal Impact Factors for each scientific discipline are available in Supplementary Table F1.

@@

  # Recode NAs to FALSE
  mutate(across(
    starts_with('has_'), ~replace_na(., FALSE) )) %>% 
  select(esi_field, starts_with("has_")) %>% 
  group_by(esi_field) %>%
  summarise(across(starts_with("has_"), list(n = sum, N = ~n()), .names = "{col}__{fn}")) %>%
  adorn_totals(name = 'OVERALL') %>%
  pivot_longer(cols = !esi_field, names_to = c('variable', '.value'), names_sep = '__', names_prefix = 'has_') %>%
  mutate(prop = n/N, percent = prop*100) %>%
  mutate(esi_abbr = case_when( # create abbreviated field labels to use in figures
    esi_field == "OVERALL" ~ "OVERALL",
    esi_field == "AGRICULTURAL SCIENCES" ~ "AGRI",
    esi_field == "BIOLOGY & BIOCHEMISTRY" ~ "BIO",       
    esi_field == "CHEMISTRY" ~ "CHEM" ,                   
    esi_field == "CLINICAL MEDICINE" ~ "MED",           
    esi_field == "COMPUTER SCIENCE" ~ "COM",             
    esi_field == "ECONOMICS & BUSINESS" ~ "ECON",         
    esi_field == "ENGINEERING" ~ "ENG",                  
    esi_field == "ENVIRONMENT_ECOLOGY" ~ "ECO",         
    esi_field == "GEOSCIENCES" ~ "GEO",                  
    esi_field == "IMMUNOLOGY" ~ "IMM",                   
    esi_field == "MATERIALS SCIENCE" ~ "MATSCI",            
    esi_field == "MATHEMATICS" ~ "MATH",                
    esi_field == "MICROBIOLOGY" ~ "MICBIO",                 
    esi_field == "MOLECULAR BIOLOGY & GENETICS" ~ "MOLBIO", 
    esi_field == "Multidisciplinary" ~ "MULTI",            
    esi_field == "NEUROSCIENCE & BEHAVIOR" ~ "NEURO",     
    esi_field == "PHARMACOLOGY & TOXICOLOGY" ~ "PHARM",    
    esi_field == "PHYSICS" ~ "PHYS",                     
    esi_field == "PLANT & ANIMAL SCIENCE" ~ "PLANT",       
    esi_field == "PSYCHIATRY_PSYCHOLOGY" ~ "PSY",       
    esi_field == "SOCIAL SCIENCES, GENERAL" ~ "SOC",     
    esi_field == "SPACE SCIENCE" ~ "SPACE"          
  )) %>%
  mutate(esi_field_with_abbr = paste0(esi_field,' (', esi_abbr,')')) %>%
  mutate(var_display = case_when( # create display versions of topic names
    variable == "guidance" ~ "Provides any statistical guidance",
    variable == "internal_guidance" ~ "Provides journal-specific statistical guidance",
    variable == "internal_guidance_section" ~ "Dedicated statistical guidance section",
    variable == "external_guidance" ~ "External statistical guidance",
    variable == "p_value" ~ "p values",
    variable == "significance" ~ "statistical significance",
    variable == "null_hypo" ~ "null hypotheses",
    variable == "sample_size" ~ "sample size",
    variable == "conf_int" ~ "confidence intervals",
    variable == "effect_size" ~ "effect sizes",
    variable == "multi_compare" ~ "multiple comparisons",
    variable == "subgroup" ~ "subgroup analyses",
    variable == "baseline_covar" ~ "baseline covariates",
    variable == "non_param" ~ "non-parametric tests",
    variable == "sensitivity" ~ "sensitivity analyses",
    variable == "model_assume" ~ "model assumptions",
    variable == "exclusion" ~ "data exclusions",
    variable == "outliers" ~ "outliers",
    variable == "missing" ~ "missing data",
    variable == "one_sided" ~ "one-tailed tests",
    variable == "bayes" ~ "Bayesian statistics",
    variable == "secondary" ~ "secondary outcomes",
    variable == "prespecify" ~ "prespecify analyses",
    variable == "cat_continuous" ~ "CCV",
    variable == "publisher_guidance" ~ "Shares publisher guidance"
  ))

@@

Out of `r sum_tab %>% filter(esi_field == "OVERALL", variable == "guidance") %>% pull(N)` journals we found that `r sum_tab %>% filter(esi_field == "OVERALL", variable == "guidance") %>% pull(n)` (`r sum_tab %>% filter(esi_field == "OVERALL", variable == "guidance") %>% pull(percent)`%) offered statistical guidance (Figure 1A; for equivalent tabular data, see Supplementary Information C). This includes `r only_ext` journals which only referred to statistical guidance in external sources (reporting guidelines or academic papers) and `r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance") %>% pull(n)` journals that provided their own guidance (of which `r crosstab_int_ext %>% filter(has_external_guidance == T, has_internal_guidance == T) %>% pull(n)` also referred to external sources). `r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance_section") %>% pull(n)` (`r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance_section") %>% pull(percent)`%) of `r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance_section") %>% pull(N)` journals had a dedicated statistical guidance section in their author instructions (Figure 1B). Journals offered statistical guidance more often in biomedical and health-related domains compared to other domains. Notably, all 15 Clinical Medicine journals offered some statistical guidance. In two domains (Computer Science and Mathematics), no journals offered any statistical guidance. Some journals shared the same publisher-level guidance, including `r publisher_nature_n` Nature journals, `r publisher_cell_n` Cell journals, and `r publisher_frontiers_n` Frontiers journals.

```{r}
# build plot for any statistical guidance
plot_any <- sum_tab_general %>%
  filter(variable == 'guidance') %>%
  arrange(percent) %>%
  mutate(esi_abbr = factor(esi_abbr, levels = c(esi_abbr[! esi_abbr == 'OVERALL'], 'OVERALL'), ordered = T)) %>%
  ggplot(aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
  ylim(0,100) +
  geom_segment(aes(xend=esi_abbr, y=0, yend=percent)) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(esi_abbr != 'OVERALL')) + 
  geom_point(size = 5, shape = 23, colour = 'black', data = . %>% filter(esi_abbr == 'OVERALL')) + 
  ggtitle('Any statistical guidance') +
  ylab('journals (%)') +
  scale_fill_domains() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none') + 
  coord_flip()

# build plot for dedicated statistical guidance section
plot_dedicated <- sum_tab_general %>%
  filter(variable == 'internal_guidance_section') %>%
  arrange(percent) %>%
  mutate(esi_abbr = factor(esi_abbr, levels = c(esi_abbr[! esi_abbr == 'OVERALL'], 'OVERALL'), ordered = T)) %>%
  ggplot(aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
  ylim(0,100) +
  geom_segment(aes(xend=esi_abbr, y=0, yend=percent)) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(esi_abbr != 'OVERALL')) + 
  geom_point(size = 5, shape = 23, colour = 'black', data = . %>% filter(esi_abbr == 'OVERALL')) + 
  ggtitle('Dedicated statistical guidance section') +
  ylab('journals (%)') +
  scale_fill_domains() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none') + 
  coord_flip()

@@

domainOrder <- sum_tab_general %>%
  filter(variable == 'guidance') %>%
  arrange(percent) %>% 
  pull(esi_abbr)

domainOrder <- c(domainOrder[! domainOrder == 'OVERALL'], 'OVERALL')

plot_any_dedicated_joint <- sum_tab_general %>%
  filter(variable %in% c('guidance', 'internal_guidance_section')) %>%
  mutate(esi_abbr = factor(esi_abbr, levels = domainOrder, ordered = T)) %>%
  ggplot(aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
  ylim(0,100) +
  geom_segment(aes(xend=esi_abbr, y=0, yend=percent), data =. %>% filter(variable == 'guidance')) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(variable == 'guidance', esi_abbr != 'OVERALL')) + 
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(variable == 'guidance', esi_abbr == 'OVERALL')) + 
  geom_point(size = 2, shape = 23, colour = 'black', data = . %>% filter(variable == 'internal_guidance_section', esi_abbr != 'OVERALL')) + 
  geom_point(size = 2, shape = 23, colour = 'black', data = . %>% filter(variable == 'internal_guidance_section', esi_abbr == 'OVERALL')) + 
  ggtitle('General statistical guidance') +
  ylab('journals (%)') +
  scale_fill_domains() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none') + 
  coord_flip()

@@

  ggplot(data = thisData, aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
    ylim(0,100) +
    geom_segment(aes(xend=esi_abbr, y=0, yend=percent)) +
    geom_point(size = 5, shape = 21, colour = 'black', data = thisData %>% filter(esi_abbr != 'OVERALL')) + 
    geom_point(size = 5, shape = 21, colour = 'black', data = thisData %>% filter(esi_abbr == 'OVERALL')) + 
    ggtitle(thisTopic) +
    ylab('journals (%)') +
    scale_fill_domains() +
    theme_apa() +
    theme(
      panel.grid.major.x = element_line(),
      axis.title.y = element_blank(),
      legend.position = 'none') + 
    coord_flip()
}

@@

@@

@@

# Discussion
Our investigation found that 48% of 330 top-ranked journals across 22 scientific disciplines provided some statistical guidance to authors, with 28% of journals having a dedicated statistical guidance section in their instructions to authors. It was far more common for journals to provide statistical guidance in biomedical and health-related disciplines relative to non-health related disciplines like the social sciences and physical sciences. Statistical guidance addressed a range of topics, and was most common for hotly debated topics: p-values, confidence intervals, sample size justification, and effect sizes. However, very few journals appeared to take particularly controversial positions, such as banning p-values or the use of statistical significance.

>>>>

```{r load_packages}
library(papaja) # for article template
library(knitr) # for literate programming
library(tidyverse) # for data munging
library(janitor) # for data munging
#library(tidylog) # inline code feedback
library(here) # for finding files
library(assertr) # for testing
library(scales) # to colour palette
library(ggforce) # helpful plotting functions
library(patchwork) # for multipanel figures
library(kableExtra) # for latex tables
```

@@

```{r set_defaults}
# define a custom colour palette that links specific colours to specific scientific disciplines across graphs

scale_fill_disciplines <- function(...){
    ggplot2:::manual_scale(
        'fill',
        values = setNames(c(hue_pal()(22),'#000000'), c(levels(factor(sum_tab_topics$esi_abbr[! sum_tab_topics$esi_abbr == 'OVERALL'])), 'OVERALL')),
        ...
    )
}

scale_fill_domains <- function(...){
    ggplot2:::manual_scale(
        'fill', 
        values = setNames(c(hue_pal()(5),'#000000'), c(levels(factor(sum_tab_topics$domain[! sum_tab_topics$domain == 'OVERALL'])), 'OVERALL')), 
        ...
    )
}
```

@@

It is unclear whether journal-based statistical guidance, advocacy, or regulation is helpful or detrimental, especially in the context of controversial statistical topics (Mayo, 2021). There continues to be heated debate among statisticians and methodologists about fundamental statistical issues, as exemplified by the diverse commentaries in a 2019 special issue of The American Statistician (Wasserstein et al., 2019). P-values continue to be vigorously attacked (Wagenmakers, 2007) and staunchly defended (Mayo, 2018), and recent years have seen competing calls to either abandon (McShane et al., 2019), redefine (Benjamin et al., 2018), or justify (Lakens et al., 2018) statistical significance. Others have advocated for a so-called “New Statistics” centered on effect size estimation and confidence intervals (Cumming, 2014) or promoted wider adoption of Bayesian statistics (Goodman, 1999; Kruschke & Liddell, 2018). 
In some cases, these debates have influenced journal policy and drastic changes in policy have sometimes backfired. For example, in 2005, in an attempt to avoid the “pitfalls of traditional statistical inference”, the journal Psychological Science endorsed a novel statistic prep (Killeen, 2005) which was subsequently adopted by the majority of publishing authors, and then abandoned under heavy criticism a few years later (Iverson et al., 2009). In 2015, the journal Basic and Applied Social Psychology introduced an outright ban on p-values and confidence intervals “because the state of the art remains uncertain” (Trafimow & Marks, 2015). An assessment of articles published in the first year after the ban argued that the absence of statistical safeguards led many authors to overstate their findings (Fricker et al., 2019).

Although particularly controversial journal policies easily catch our attention, they may not be representative. Currently there is limited empirical data documenting the prevalence and content of statistical guidance for authors issued by scientific journals. Such data may help to inform debates about the appropriate role of journal policy in addressing statistical issues (Mayo, 2021) as well as identify gaps in journal-based statistical guidance within and across scientific disciplines. Some previous research has addressed this topic and suggested that there is probably large room for improvement. For example, Schriger et al. (2006) reported that 39% of 166 leading medical journals provided statistical guidance to authors. Topics addressed included p-values (20%), confidence intervals (14%), statistical power (10%), multiple testing (5%), modeling (4%), sensitivity analysis (4%), and Bayesian methods (1%). Recently, Malicki et al. (2019) used a text-mining approach to search for a limited set of terms related to Bayes factors, confidence intervals, effect sizes, and sample size calculations in instructions to authors provided by 835 journals across a range of scientific disciplines. The prevalence of any statistical guidance, defined by these terms, was 6% across all journals. Another empirical evaluation (Malicki et al., 2020) found that none of 57 preprint servers provided any statistical advice. These three studies provide some insight into the prevalence and content of statistical guidance offered to authors; however, Schriger et al. (2006) was limited to medical journals, Malicki et al. (2020) was limited to preprint servers, and Malicki et al. (2019) focused on only a few statistical topics.

@@

Across all 22 scientific disciplines (n = 330 journals), the median 2017 Journal Impact Factor was `r allFieldChar %>% pull(Median_jif)` (IQR = `r allFieldChar %>% pull(IQR_jif)`; range `r allFieldChar %>% pull(Min_jif)` - `r allFieldChar %>% pull(Max_jif)`). Journal Impact Factors for each scientific discipline are available in Supplementary Table F1.

@@

  # Recode NAs to FALSE
  mutate(across(
    starts_with('has_'), ~replace_na(., FALSE) )) %>% 
  select(esi_field, domain, starts_with("has_")) %>% 
  group_by(esi_field, domain) %>%
  summarise(across(starts_with("has_"), list(n = sum, N = ~n()), .names = "{col}__{fn}")) %>%
  adorn_totals(name = 'OVERALL') %>%
  pivot_longer(cols = !c(esi_field,domain), names_to = c('variable', '.value'), names_sep = '__', names_prefix = 'has_') %>%
  mutate(prop = n/N, percent = prop*100) %>%
  mutate(domain = ifelse(esi_field == "OVERALL", "OVERALL", domain)) %>%
  mutate(esi_abbr = case_when( # create abbreviated field labels to use in figures
    esi_field == "OVERALL" ~ "OVERALL",
    esi_field == "AGRICULTURAL SCIENCES" ~ "AGRI",
    esi_field == "BIOLOGY & BIOCHEMISTRY" ~ "BIO",       
    esi_field == "CHEMISTRY" ~ "CHEM" ,                   
    esi_field == "CLINICAL MEDICINE" ~ "MED",           
    esi_field == "COMPUTER SCIENCE" ~ "COM",             
    esi_field == "ECONOMICS & BUSINESS" ~ "ECON",         
    esi_field == "ENGINEERING" ~ "ENG",                  
    esi_field == "ENVIRONMENT & ECOLOGY" ~ "ECO",         
    esi_field == "GEOSCIENCES" ~ "GEO",                  
    esi_field == "IMMUNOLOGY" ~ "IMM",                   
    esi_field == "MATERIALS SCIENCE" ~ "MATSCI",            
    esi_field == "MATHEMATICS" ~ "MATH",                
    esi_field == "MICROBIOLOGY" ~ "MICBIO",                 
    esi_field == "MOLECULAR BIOLOGY & GENETICS" ~ "MOLBIO", 
    esi_field == "MULTIDISCIPLINARY" ~ "MULTI",            
    esi_field == "NEUROSCIENCE & BEHAVIOR" ~ "NEURO",     
    esi_field == "PHARMACOLOGY & TOXICOLOGY" ~ "PHARM",    
    esi_field == "PHYSICS" ~ "PHYS",                     
    esi_field == "PLANT & ANIMAL SCIENCE" ~ "PLANT",       
    esi_field == "PSYCHIATRY & PSYCHOLOGY" ~ "PSY",       
    esi_field == "SOCIAL SCIENCES (GENERAL)" ~ "SOC",     
    esi_field == "SPACE SCIENCE" ~ "SPACE"          
  )) %>%
  mutate(esi_field_with_abbr = paste0(esi_field,' (', esi_abbr,')')) %>%
  mutate(var_display = case_when( # create display versions of topic names
    variable == "guidance" ~ "Provides any statistical guidance",
    variable == "internal_guidance" ~ "Provides journal-specific statistical guidance",
    variable == "internal_guidance_section" ~ "Dedicated statistical guidance section",
    variable == "external_guidance" ~ "External statistical guidance",
    variable == "p_value" ~ "p values",
    variable == "significance" ~ "statistical significance",
    variable == "null_hypo" ~ "null hypotheses",
    variable == "sample_size" ~ "sample size",
    variable == "conf_int" ~ "confidence intervals",
    variable == "effect_size" ~ "effect sizes",
    variable == "multi_compare" ~ "multiple comparisons",
    variable == "subgroup" ~ "subgroup analyses",
    variable == "baseline_covar" ~ "baseline covariates",
    variable == "non_param" ~ "non-parametric tests",
    variable == "sensitivity" ~ "sensitivity analyses",
    variable == "model_assume" ~ "model assumptions",
    variable == "exclusion" ~ "data exclusions",
    variable == "outliers" ~ "outliers",
    variable == "missing" ~ "missing data",
    variable == "one_sided" ~ "one-tailed tests",
    variable == "bayes" ~ "Bayesian statistics",
    variable == "secondary" ~ "secondary outcomes",
    variable == "prespecify" ~ "prespecify analyses",
    variable == "cat_continuous" ~ "CCV",
    variable == "publisher_guidance" ~ "Shares publisher guidance"
  ))

@@

```{r}
# domain-level summary

sum_tab_domain <- sum_tab %>% 
  group_by(domain, variable) %>%
  summarise(n = sum(n), N = sum(N)) %>%
  mutate(prop = n/N, percent = n/N*100)

any_guidance_healthlife <- sum_tab_domain %>% filter(domain == 'HEALTH & LIFE SCIENCES', variable == 'guidance')
any_guidance_multi <- sum_tab_domain %>% filter(domain == 'MULTIDISCIPLINARY', variable == 'guidance')
any_guidance_social <- sum_tab_domain %>% filter(domain == 'SOCIAL SCIENCES', variable == 'guidance')
any_guidance_physical <- sum_tab_domain %>% filter(domain == 'PHYSICAL SCIENCES', variable == 'guidance')
any_guidance_formal <- sum_tab_domain %>% filter(domain == 'FORMAL SCIENCES', variable == 'guidance')
```

The frequency of journal author instructions providing statistical guidance varied considerably across domains (Health and Life Sciences: `r any_guidance_healthlife %>% pull(n)` of `r any_guidance_healthlife %>% pull(N)` journals, `r any_guidance_healthlife %>% pull(percent) %>% round()`%; Multidisciplinary: `r any_guidance_multi %>% pull(n)` of `r any_guidance_multi %>% pull(N)` journals, `r any_guidance_multi %>% pull(percent) %>% round()`%; Social Sciences: `r any_guidance_social %>% pull(n)` of `r any_guidance_social %>% pull(N)` journals, `r any_guidance_social %>% pull(percent) %>% round()`%; Physical Sciences: `r any_guidance_physical %>% pull(n)` of `r any_guidance_physical %>% pull(N)` journals, `r any_guidance_physical %>% pull(percent) %>% round()`; Formal Sciences: `r any_guidance_formal %>% pull(n)` of `r any_guidance_formal %>% pull(N)` journals, `r any_guidance_formal %>% pull(percent) %>% round()`.

Out of `r sum_tab %>% filter(esi_field == "OVERALL", variable == "guidance") %>% pull(N)` journals we found that `r sum_tab %>% filter(esi_field == "OVERALL", variable == "guidance") %>% pull(n)` (`r sum_tab %>% filter(esi_field == "OVERALL", variable == "guidance") %>% pull(percent)`%) offered statistical guidance (Figure 1A; for equivalent tabular data, see Supplementary Information C). This includes `r only_ext` journals which only referred to statistical guidance in external sources (reporting guidelines or academic papers) and `r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance") %>% pull(n)` journals that provided their own guidance (of which `r crosstab_int_ext %>% filter(has_external_guidance == T, has_internal_guidance == T) %>% pull(n)` also referred to external sources). `r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance_section") %>% pull(n)` (`r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance_section") %>% pull(percent)`%) of `r sum_tab %>% filter(esi_field == "OVERALL", variable == "internal_guidance_section") %>% pull(N)` journals had a dedicated statistical guidance section in their author instructions (Figure 1B). Journals offered statistical guidance more often in Health and Life Sciences compared to other domains. Notably, all 15 Clinical Medicine journals offered some statistical guidance. In two domains (Computer Science and Mathematics), no journals offered any statistical guidance. Some journals shared the same publisher-level guidance, including `r publisher_nature_n` Nature journals, `r publisher_cell_n` Cell journals, and `r publisher_frontiers_n` Frontiers journals.

```{r}
# build plot for any statistical guidance
plot_any <- sum_tab_general %>%
  filter(variable == 'guidance') %>%
  arrange(percent) %>%
  mutate(esi_abbr = factor(esi_abbr, levels = c(esi_abbr[! esi_abbr == 'OVERALL'], 'OVERALL'), ordered = T)) %>%
  ggplot(aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
  ylim(0,100) +
  geom_segment(aes(xend=esi_abbr, y=0, yend=percent)) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(esi_abbr != 'OVERALL')) + 
  geom_point(size = 5, shape = 23, colour = 'black', data = . %>% filter(esi_abbr == 'OVERALL')) + 
  ggtitle('Any statistical guidance') +
  ylab('journals (%)') +
  scale_fill_disciplines() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none') + 
  coord_flip()

# build plot for dedicated statistical guidance section
plot_dedicated <- sum_tab_general %>%
  filter(variable == 'internal_guidance_section') %>%
  arrange(percent) %>%
  mutate(esi_abbr = factor(esi_abbr, levels = c(esi_abbr[! esi_abbr == 'OVERALL'], 'OVERALL'), ordered = T)) %>%
  ggplot(aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
  ylim(0,100) +
  geom_segment(aes(xend=esi_abbr, y=0, yend=percent)) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(esi_abbr != 'OVERALL')) + 
  geom_point(size = 5, shape = 23, colour = 'black', data = . %>% filter(esi_abbr == 'OVERALL')) + 
  ggtitle('Dedicated statistical guidance section') +
  ylab('journals (%)') +
  scale_fill_disciplines() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none') + 
  coord_flip()

@@

disciplineOrder <- sum_tab_general %>%
  filter(variable == 'guidance') %>%
  arrange(percent) %>% 
  pull(esi_abbr)

disciplineOrder <- c(disciplineOrder[! disciplineOrder == 'OVERALL'], 'OVERALL')

plot_any_dedicated_joint <- sum_tab_general %>%
  filter(variable %in% c('guidance', 'internal_guidance_section')) %>%
  mutate(esi_abbr = factor(esi_abbr, levels = disciplineOrder, ordered = T)) %>%
  ggplot(aes(x=esi_abbr, y = percent, fill = esi_abbr)) +
  ylim(0,100) +
  geom_segment(aes(xend=esi_abbr, y=0, yend=percent), data =. %>% filter(variable == 'guidance')) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(variable == 'guidance', esi_abbr != 'OVERALL')) + 
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(variable == 'guidance', esi_abbr == 'OVERALL')) + 
  geom_point(size = 2, shape = 23, colour = 'black', data = . %>% filter(variable == 'internal_guidance_section', esi_abbr != 'OVERALL')) + 
  geom_point(size = 2, shape = 23, colour = 'black', data = . %>% filter(variable == 'internal_guidance_section', esi_abbr == 'OVERALL')) + 
  ggtitle('General statistical guidance') +
  ylab('journals (%)') +
  scale_fill_disciplines() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none') + 
  coord_flip()

```{r}
### REVISED PLOTS ###

# first make a data frame with overall data for each domain

domain_overalls <- sum_tab_general %>% 
  filter(esi_field != "OVERALL") %>% # remove previous overall summary
  group_by(domain, variable, var_display) %>%
  summarise(n = sum(n), N = sum(N)) %>%
  mutate(prop = n/N, percent = n/N*100, esi_abbr = paste(domain,'(ALL)'), esi_field = paste(domain,'(ALL)'), esi_field_with_abbr = paste(domain,'(ALL)'), priority = 2)

forPlot <- sum_tab_general %>% 
  filter(esi_field != "OVERALL") %>% # remove previous overall summary 
  mutate(priority = 1) %>%
  rbind(domain_overalls)

# set ordering of disciplines and domains
domainOrder <- domain_overalls %>%
  filter(variable == 'guidance') %>%
  arrange(desc(percent)) %>% 
  pull(domain)

axesOrder <- forPlot %>%
  filter(variable == 'guidance', esi_field != "MULTIDISCIPLINARY") %>%
  mutate(domain = factor(domain, levels = domainOrder, ordered = T)) %>%
  arrange(domain, priority, percent) %>% 
  pull(esi_field)

ready <- forPlot %>% 
  filter(esi_field != "MULTIDISCIPLINARY",
    variable %in% c('guidance', 'internal_guidance_section')) %>%
  mutate(esi_field = factor(esi_field, levels = axesOrder, ordered = T),
         domain = factor(domain, levels = domainOrder, ordered = T))

plot_any_dedicated_joint <- ready %>%
  ggplot(aes(y=esi_field, x = percent, fill = domain)) +
  xlim(0,100) +
  ggforce::facet_col(facets = vars(domain), 
                     scales = "free_y", 
                     space = "free") +
  geom_segment(aes(yend=esi_field, x=0, xend=percent), data =. %>% filter(variable == 'guidance')) +
  geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(variable == 'guidance')) + 
  geom_point(size = 2, shape = 23, colour = 'black', data = . %>% filter(variable == 'internal_guidance_section')) + 
  geom_col(data = . %>% filter(variable == 'guidance', grepl('ALL', esi_field)), alpha = .2) + 
  xlab('journals (%)') +
  scale_fill_domains() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none',
    #strip.text = element_text(hjust = 0),
    strip.text.x = element_blank())

@@

  ggplot(data = thisData, aes(x=esi_abbr, y = percent, fill = domain)) +
    ylim(0,100) +
    geom_segment(aes(xend=esi_abbr, y=0, yend=percent)) +
    geom_point(size = 5, shape = 21, colour = 'black', data = thisData %>% filter(esi_abbr != 'OVERALL')) + 
    geom_point(size = 5, shape = 21, colour = 'black', data = thisData %>% filter(esi_abbr == 'OVERALL')) + 
    ggtitle(thisTopic) +
    ylab('journals (%)') +
    scale_fill_domains() +
    theme_apa() +
    theme(
      panel.grid.major.x = element_line(),
      axis.title.y = element_blank(),
      legend.position = 'none') + 
    coord_flip()
}

@@

```{r}
# REVISED PLOTS

sum_tab_topics_domains <- sum_tab_topics %>% 
  group_by(domain, topic_display) %>% 
  summarise(n = sum(n), N = sum(N)) %>% 
  mutate(prop = n/N, percent = n/N*100)

# get order of topics in terms of most frequently mentioned
topics_ordered <- sum_tab_topics_domains %>%
  filter(domain == 'OVERALL') %>%
  arrange(percent) %>%
  pull(topic_display)

sum_tab_topics_domains <- sum_tab_topics_domains %>%
  mutate(topic_display = factor(topic_display, levels = topics_ordered, ordered = T))

customDomains <- c("HEALTH & LIFE SCIENCES"="HEALTH & LIFE SCIENCES", 
                      "MULTIDISCIPLINARY"="MULTI- DISCIPLINARY", 
                      "PHYSICAL SCIENCES"="PHYSICAL SCIENCES", 
                      "SOCIAL SCIENCES"="SOCIAL SCIENCES")

specific_fig_new <- sum_tab_topics_domains %>%
  filter(domain %notin% c('FORMAL SCIENCES','OVERALL')) %>% 
  ggplot(aes(y = topic_display, x = percent, fill = domain)) +
  facet_wrap(.~domain, nrow = 1, labeller = as_labeller(customDomains, multi_line = T, default=label_wrap_gen(10))) +
  #facet_wrap(.~domain, nrow = 1, labeller = label_wrap_gen(width = 2, multi_line = TRUE)) +
  xlim(0,60) +
  xlab('journals (%)') +
  geom_segment(aes(yend=topic_display, x=0, xend=percent)) +
  geom_point(size = 5, shape = 21, colour = 'black') +
  scale_fill_domains() +
  theme_apa() +
  theme(
    panel.grid.major.x = element_line(),
    axis.title.y = element_blank(),
    legend.position = 'none',
    strip.background = 
  )

```{r specifictopicsfignew, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 8, fig.height = 7, fig.cap = "Caption here"}
specific_fig_new
```

@@

```{r}
sum_tab_domain %>% filter(variable == 'external_guidance') %>% arrange(desc(percent))
```

@@

# Discussion
Our investigation found that 48% of 330 top-ranked journals across 22 scientific disciplines provided some statistical guidance to authors, with 28% of journals having a dedicated statistical guidance section in their instructions to authors. It was far more common for journals to provide statistical guidance in Health and Life Sciences relative to non-health related disciplines like the social sciences and physical sciences. Statistical guidance addressed a range of topics, and was most common for hotly debated topics: p-values, confidence intervals, sample size justification, and effect sizes. However, very few journals appeared to take particularly controversial positions, such as banning p-values or the use of statistical significance.
